---
title: "Example of labelr"
output: html_notebook
---

Here's an example of how the labeler works. You'll need to import your specimen list as well as relevant metadata about those data.

```{r}
library(here)
library(tidyverse)
```


# Import data

Requires specimen data in .csv form.


```{r import data}
data.path= here("sample datasets")

biofuels_det=read.csv(paste(data.path,"determination.df.csv", sep = "/"), stringsAsFactors = F)

# import some specimen data in
gradients= read.csv(paste(data.path,"clean-networks.csv", sep = "/"), stringsAsFactors = F)

# if metadata lives in separate file
siteinfo=read.csv(paste(data.path,"gradients_siteinfo.csv", sep = "/"), stringsAsFactors = F)

```

# create locality labels using: `locality.label`

```{r locality label function}
source("locality.label.R")
```

Maybe will need to concantentate some dfs together (can do this outside of R or within as in this example)

```{r}
# can filter and select df as needed, eg. for our dataset we only want the subset of this df that has specimen numbers
gradients= gradients %>% 
  filter(!is.na(specimen_number))

# join site info to the specimen data
gradients.plus.metadata= left_join(gradients, siteinfo)

# paste lat and long together
gradients.plus.metadata$lat.long=paste (gradients.plus.metadata$latitude, "N," , gradients.plus.metadata$longitude,'W')

```


Ok now apply the locality label function

This locality label function needs these inputs:
- df
- spec.num: column that identifies specimens uniquely,
- country
- state / territory / province
- county
- general geographic location
- specific geographic location
- date
- collector

```{r}
loc.lab=locality.label(gradients.plus.metadata, "specimen_number", "country", "state", "county", "generalgeo", "lat.long", "date", "who")

write.table(loc.lab, file = "locality_label.csv", sep = ",", col.names = F, row.names = F, append=FALSE)

```


# create determination labels using: `determination.label`

```{r determination label function}
source("determination.label.R")
```

This determination label function needs these inputs:
- df
- id: who identified,
- authority: taxonomic authority for that species
- year identified

+ You can name these columns anything in your df (in the example given they are `genus.species`, `auth` and so on)

```{r}
det.labs= determination.label(biofuels_det, "genus.species", "auth", "ident", "Year")

write.table(det.labs, file = "determination_labels.csv", sep = ",", col.names = F, row.names = F, append=FALSE)
```

